%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Maria Luiza Linhares Dantas
% 
% This is an example of a very complete CV using the 'moderncv' package
% and the 'timeline' package. For more information on those, please
% access: 
% https://www.ctan.org/tex-archive/macros/latex/contrib/moderntimeline
% https://www.ctan.org/tex-archive/macros/latex/contrib/moderncv
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\title{Curriculum Vitae SandBox}
\documentclass[11pt, a4paper, roman]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue} 
\pagenumbering{roman}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.87, top=2cm]{geometry}    % Width of the entire CV
\setlength{\hintscolumnwidth}{2.2cm} % Width of the timeline on your left
\usepackage{mathptmx}
\usepackage{pdfpages/pdfpages}
\usepackage{moderntimeline/moderntimeline}
\usepackage{xpatch/xpatch}
\usepackage{color, graphicx}
\tlmaxdates{2007}{2016}              % Beginning and start of your timeline       

\usepackage[none]{hyphenat}

\usepackage{lastpage}
% \lhead{\itshape{Facebook AI Research Residency Program (2018)}}
% \rhead{\addressfont\itshape{\textbf{Email Address: tpsatish95@gmail.com}}}

% \lfoot{\itshape{The Swiss AI Lab IDSIA and The University of Lugano (USI), Switzerland}}
\rfoot{\addressfont\itshape{Page \thepage\ }}

\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}


\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\newcommand{\cvreferencecolumn}[2]{%
  \cvitem[0.8em]{}{%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#2\end{minipage}%
    }%
}

\newcommand{\cvreference}[8]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{\href{mailto:#6}{\nolinkurl{#6}}}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7\newline}
    \ifthenelse{\equal{#8}{}}{}{\mobilephonesymbol~#8}}


% Personal Information
\name{Satish Palaniappan}{}
% \title{\emph{Résumé}} 
\title{\emph{Curriculum Vitae}} 
\social[github]{tpsatish95}   % optional, remove / comment the line if not wanted           
\social[linkedin]{satishpalaniappan}  % optional, remove / comment the line if not wanted   
\email{spalani2@cs.jhu.edu}                % optional, remove / comment the line if not wanted
\phone[mobile]{+1~(412) 499-1316}      

\begin{document}
\pagenumbering{arabic}
\makecvtitle
\vspace*{-6mm}

\section{Interests}
\cventry{}{Machine Learning, Deep Learning, Computer Vision, Natural Language Processing, and Algorithm Design}{}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Educational Background}
\cventry{2018-Present}{Johns Hopkins University (JHU)}{Whiting School of Engineering (WSE), \newline Masters in Computer Science}{}{}{}
\cventry{2012-2016}{Anna University}{Sri Sivasubramaniya Nadar College of Engineering (SSN CE), \newline Bachelors in Computer Science and Engineering, \emph{\textbf{CGPA}: 8.56/10}}{}{}{}
% \cventry{2010-2012}{TVS Matriculation Higher Secondary School (TVS M HSS)}{\newline 12th Grade (Higher Secondary Certificate), \emph{\textbf{Score}: 98\%}}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Research Experience}
\cventry{Dec,2015 - Present}{Research Assistant}{\textsc{Institute of Mathematical Sciences, Chennai}}{}{}{
\textbf{Optical Character Recognition on Indus Scripts} \href{https://github.com/tpsatish95/indus-script-ocr}{{\color{blue!70}{[link]}}} \href{https://arxiv.org/abs/1702.00523}{\color{blue!70}{[paper]}}
\newline
under Prof. Ronojoy Adhikari, Department of Physics
\begin{itemize}
\item Recognize Indus script symbols from scans and photographs of ancient Harappan civilization artifacts.
\item \textbf{Techniques:} Convolutional Neural Networks (CNN), GoogLeNet, Transfer Learning, and Selective Search.
\item \textbf{Media Coverage:} \href{http://www.thehindu.com/sci-tech/science/chennai-team-taps-ai-to-read-indus-script/article17448690.ece}{{\color{blue!70}{\textit{The Hindu}}}}, \href{https://www.theverge.com/2017/1/25/14371450/indus-valley-civilization-ancient-seals-symbols-language-algorithms-ai\#EQQA6r}{{\color{blue!70}{\textit{The Verge}}}} (small piece), \href{http://timesofindia.indiatimes.com/city/chennai/app-may-help-decipher-indus-valley-symbols/articleshow/57281369.cms}{{\color{blue!70}{\textit{Times of India}}}}, and \href{http://www.sbs.com.au/yourlanguage/tamil/en/content/app-decipher-ancient-symbols?language=en}{{\color{blue!70}{\textit{SBS Radio - Australia}}}}.
\end{itemize}}

\cventry{Dec,2014}{Research Intern}{\textsc{Carnegie Mellon University (IPTSE Winter School)}}{}{}{
\textbf{Text Based Emotion Recognition System} \href{https://github.com/tpsatish95/emotion-detection-from-text}{\color{blue!70}{[link]}}
\newline
under Prof. Bhiksha Raj and Prof. Rita Singh, Department of Computer Science
\begin{itemize}
\item Classify any textual data, using histograms built based on word2vec word/phrase clusters, into one of the 7 chosen basic emotions.
\item \textbf{Techniques:} Word2Vec, Latent Dirichlet Allocation (LDA), K-means, Support Vector Machines (SVM), Probabilistic N-Gram models, Multinomial Naive Bayes.
\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Industry Research Experience}
\cventry{Jun,2016 - Present}{Software Engineer}{\textsc{Qube Cinema Technologies, India}}{}{}{
under Rajesh Ramachandran, Chief Technology Officer \& President
\begin{itemize}
\item \textbf{Projects:} 
\begin{itemize}
\item Scalable \textbf{viewer-demographics mining engine}, that can extract information such as count, age, gender, and emotions of the movie watchers, from low-light images of a theatre's auditorium.
\item Real-time, adaptive, \textbf{resource allocation and optimization algorithm}, for making business decisions intelligently and maximizing profits.
\item \textbf{Smart-bot for automatically syncing theatre databases} across the globe, into one unified format.
\end{itemize}
\item \textbf{Techniques and Tools:} CNNs with feedback-based learning, Semantic similarity models built over digital-cinema domain data, Camera Calibration, Amazon Web Services, Flask+uWSGI+Nginx servers.
\item \textbf{Algorithms:} Knapsack Problem, Minimum Cost Flow (Transportation) Problem, Pruned Search Trees, Recursive and Linked Interval Trees.
\end{itemize}}

\cventry{May,2015 - Jul,2015}{Data Scientist - Intern}{\textsc{Serendio Inc., India}}{}{}{
under Ravi Condamoor, Chief Executive Officer
\begin{itemize}
\item \textbf{Projects:}
\begin{itemize}
\item Universal multi-domain \textbf{sentiment scorer} for text  \href{https://github.com/tpsatish95/Universal-MultiDomain-Sentiment-Classifier}{\color{blue!70}{[link]}}.
\item \textbf{Topic composition modeling} using hierarchical K-Means and semantic word clusters \href{https://github.com/tpsatish95/Topic-Modeling-Social-Network-Text-Data}{\color{blue!70}{[link]}}.
\item \textbf{Internet slang text parser} \href{https://github.com/tpsatish95/SocialTextFilter}{\color{blue!70}{[link]}}.
\end{itemize}
\item \textbf{Techniques and Tools:}  Gensim, Tf-idf features, Bagging and Boosting, CMU ARK's Twokenize, Rake - Keyword Extractor, Web Crawlers, etc.
\item Serendio Inc.'s \textbf{campus ambassador} at SSN CE.
\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Papers, Patents and Theses}
\cvitem{Feb,2017}{Paper titled, "\textbf{Deep Learning the Indus Script}", PLoS ONE (submitted), arXiv:\href{https://arxiv.org/pdf/1702.00523.pdf}{\color{blue!70}{1702.00523v1}}.}

\cvitem{Apr,2016}{Undergraduate thesis titled, "\textbf{Automated Scenario Description for Images}", Anna University. \href{https://github.com/tpsatish95/image-captioning/blob/master/report.pdf}{\color{blue!70}{[link]}}}

\cvitem{Apr,2015}{Paper titled, "\textbf{Home Automation Systems - A Study}", International Journal of Computer Applications (IJCA), Vol. 116 - No.11, Reference ID: pxc3902601. \href{http://research.ijcaonline.org/volume116/number11/pxc3902601.pdf}{\color{blue!70}{[link]}} \newline
- \textbf{Best paper award}, SSN UG paper presentation event. 13 Citations \href{https://scholar.google.co.in/citations?user=gNr8v84AAAAJ&hl=en&oi=ao}{\color{blue!70}{[google scholar]}}.}

\cvitem{Oct,2015}{Patent filed, titled, "\textbf{Universally Compatible and Accessible, Software Controlled, Expandable Home Automation System, for Energy Conservation and the Differently-Abled}", Reference ID: 5729/CHE/2015. \href{https://www.youtube.com/watch?v=O-L_uSHqQvQ}{\color{blue!70}{[video report]}}, \href{http://ipindiaservices.gov.in/PublicSearch/}{[patent search link]}.} 

\cvitem{Apr,2015}{Paper titled, "\textbf{Automated Meter Reading System - A Study}", International Journal of Computer Applications (IJCA), Vol. 116 - No.18, Reference ID: pxc3902783. \href{http://research.ijcaonline.org/volume116/number18/pxc3902783.pdf}{\color{blue!70}{[link]}}}

\cvitem{Dec,2014}{Poster presented, titled, "\textbf{Text Based Emotion Recognition System}", CMU-IPTSE Winter School, at NITK Surathkal. \href{https://github.com/tpsatish95/emotion-detection-from-text/blob/master/docs/poster.jpg}{\color{blue!70}{[link]}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\cventry{Jun,2015 - Apr,2016}{Automated Scenario Description for Images}{Undergraduate thesis}{\textsc{Anna University}}{}{under Prof. Milton R.S., Department of Computer Science and Engg., SSN CE, \href{https://github.com/tpsatish95/image-captioning}{\color{blue!70}{[link]}}, \href{https://github.com/tpsatish95/image-captioning/blob/master/report.pdf}{\color{blue!70}{[thesis]}}.
\begin{itemize}
\item Harnessed object identification and scene classification techniques to automatically generate natural language descriptions of images. 
\end{itemize}}

\cventry{Mar,2018}{Distributed Panorama Construction of High Resolution UAV Imagery Using Public Compute Nodes}{Department of Space (Indian Space Research Organization)}{\textsc{Smart India Hackathon 2018 (Software Edition)}}{\href{https://www.youtube.com/watch?v=iWw4_Ub2lPw&feature=youtu.be}{\color{blue!70}{[video]}}, \href{https://docs.google.com/presentation/d/1P-qX7qzGlI3vbvqG5tUDFrUdL1Y8diXQL0QLaqvQ3pk/edit?usp=sharing}{\color{blue!70}{[link]}}}{
\begin{itemize}
\item The solution devised for this problem was based on an amalgamation of concepts from Cloud Computing, Parallel Computing, Mobile Computing and Computer Vision.
\item Our team secured the first place in this nation-wide hackathon along with a cash award of Rs.1,00,000.
\item \textbf{Media Coverage:} \href{https://www.thehindu.com/todays-paper/tp-national/tp-tamilnadu/5-teams-from-ssn-college-win-prizes/article23461319.ece}{{\color{blue!70}{\textit{The Hindu}}}}, \href{https://timesofindia.indiatimes.com/city/ahmedabad/six-winners-emerge-from-smart-india-hackathon/articleshow/63561717.cms?utm_source=whatsapp&utm_medium=social&utm_campaign=TOIMobile}{{\color{blue!70}{\textit{Times of India}}}}, \href{https://www.facebook.com/gtuoffice/videos/1786668221397028/?t=8798}{{\color{blue!70}{\textit{Gujarat Technological University}}}}, and \href{http://www.ssn.edu.in/?page_id=15246}{{\color{blue!70}{\textit{SSN CE}}}}
\end{itemize}}

\cventry{Sep,2014 - Jun,2015}{Software Controlled Appliances for Energy Conservation and Differently Abled people}{Funded research project}{\textsc{SSN Innovation Center}}{\href{https://github.com/tpsatish95/home-automation-system}{\color{blue!70}{[link]}}}{ 
\begin{itemize}
\item Built a Raspberry Pi powered, adaptive and modular system, to provide planet-wide access to electronic appliances using software interfaces (mobile apps) via the Internet cloud. (Internet of Things)
\end{itemize}
}

\cventry{Mar,2015}{Intelligent Food Resources Monitoring \& Management system (PingMyFood - The Food Network)}{Startup venture}{\textsc{SSN Entrepreneurship Development Cell}}{\href{https://github.com/tpsatish95/PingMyFood}{\color{blue!70}{[link]}}}{ 
\begin{itemize}
\item Built a social network for food sharing. It collaboratively mitigates food resource wastage by routing the surplus food to food deficit regions and also allows everyone to share food with each other.
\item Powered by an intelligent, cuisine, food, and chef based topic modeling and quality rating system.
\end{itemize}
}

\cventry{Feb,2015 - Dec,2015}{Automated Scoring of YouTube videos from Pairwise Comparisons and Metadata based on Degree of Funniness}{Side project}{\href{https://github.com/tpsatish95/Youtube-Comedy-Comparison}{\color{blue!70}{[link]}}}{}{   
\begin{itemize}
\item Built a regression model, that scores YouTube videos based on their degree of funniness with just the non-video metadata such as the title, description, and comments.
\item Developed a heuristic for converting the pairwise comparisons into unified overall rankings across videos.
\end{itemize}
}

\cventry{Sep,2015}{Market Segmentation based on Customer Activity}{Business Analytics Hackathon}{\textsc{SSN School of Advanced Career Education}}{\href{https://github.com/tpsatish95/market-segmentation-based-on-human-activity}{\color{blue!70}{[link]}}}{ 
\begin{itemize}
\item Developed a market segmentation algorithm by clustering human activity patterns tracked and predicted using smartphone data such as accelerometer \& gyroscope readings.
\end{itemize}
}

\cventry{Mar,2017}{Barcode based Hardware Inventory Management}{Department of Posts}{\textsc{Smart India Hackathon 2017}}{\href{https://github.com/tpsatish95/talks/blob/master/Barcode\%20based\%20Hardware\%20Inventory\%20Management\%20-\%20TechWhiz\%20-\%20Smart\%20India\%20Hackathon\%202017.pdf}{\color{blue!70}{[link]}}}{
\begin{itemize}
\item Our team secured the 2nd Runner-up position in this nation-wide hackathon along with a cash award of Rs.50,000.
\end{itemize}}

\cventry{Dec,2013}{Regional Transport Office (RTO) Management System}{Software Development Engineer - Internship}{\textsc{Ramco Systems, India}}{\href{https://github.com/tpsatish95/misc-projects-and-experiments/tree/master/redundant_databases_ramco_systems}{\color{blue!70}{[link]}}}{
\begin{itemize}
\item Worked on building and managing fail-safe redundant database systems.
\item Learned about Enterprise Resource Management (ERP) on cloud.
\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards and Achievements}

\cvitem{}{- \textbf{Merit Scholarship (Full)} for Excellence in Academics, $1^{st}$ Year, worth Rs.105,000, SSN CE.}
\cvitem{}{- \textbf{Microsoft Research} certified, for proficiency in "Design and Analysis of Algorithms".}
\cvitem{}{- \textbf{Top 4} in the state and \textbf{Top 100} across the country,  \textbf{Aspirations 2020} programming contest, \textbf{Infosys}.}
\cvitem{}{-  \textbf{Industry Mentor} for two consecutive years at the \textbf{Smart India Hackathon} (world's largest hackathon), organized by the \textbf{Government of India}.}
\cvitem{}{- \textbf{Outstanding Student Organizer Award}, SSN ACM Student Chapter.}
\cvitem{}{- \textbf{Young Achiever Award} for Excellence in Academics, Tractors And Farm Equipments Ltd., India.}
\cvitem{}{- All India Rank of 456 in the 14th \textbf{National Science Olympiad}.}
\cvitem{}{- Rated as an \textbf{excellent programmer in "C"} by NIIT.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Talks}
\cventry{}{- Deep learning based OCR engine for the Indus script}{}{}{}{
\begin{itemize}
\item \textbf{Venues:} Indian Deep Learning Initiative (IDLI) \href{https://github.com/tpsatish95/talks/blob/master/Deep\%20learning\%20based\%20OCR\%20engine\%20for\%20the\%20Indus\%20script\%20-\%20IDLI\%20Talk.pdf}{\color{blue!70}{[slide deck]}} \href{https://www.youtube.com/watch?v=qPF1oR9yMNY}{\color{blue!70}{[video]}} \href{https://www.facebook.com/groups/idliai/}{\color{blue!70}{[link]}}, ThoughtWorks Geek Night \href{https://github.com/tpsatish95/talks/blob/master/Deep\%20learning\%20based\%20OCR\%20engine\%20for\%20the\%20Indus\%20script\%20-\%20TW\%20Geek\%20Night.pdf}{\color{blue!70}{[slide deck]}} \href{https://www.youtube.com/watch?v=g7v4QaCD-UQ}{\color{blue!70}{[video]}} \href{https://twchennai.github.io/geeknight/edition-43.html}{\color{blue!70}{[link]}}, ChennaiPy \href{http://chennaipy.org/may-2017-meet-minutes.html}{\color{blue!70}{[link]}}, Anthill Inside 2017 \href{https://anthillinside.talkfunnel.com/2017/15-deep-learning-based-ocr-engine-for-the-indus-scrip}{\color{blue!70}{[proposal]}}.
\end{itemize}}

\cventry{}{- Pokemon World and The Indus Valley Civilisation - The Analogy}{}{}{}{
\begin{itemize}
\item \textbf{Venues:} Faculty Development Program, AICTE - SSN CE \href{https://docs.google.com/presentation/d/1YI6VKB-lWh5x7q23zfAEALaPbpKu9OqYYnwRIzwvZLg/edit?usp=sharing}{\color{blue!70}{[slide deck]}}, Qube Cinema Technologies - Offsite 2017 {\color{blue!70}{slide deck}} \href{https://docs.google.com/presentation/d/1C2peTKpVMQM1KuadNgPzR7dg_R7cqexP0B8VdifsfX4/edit?usp=sharing}{\color{blue!70}{[V1}}, \href{https://docs.google.com/presentation/d/1FSodM6Qbzglhrn_VizEul-MkerEBhEQIHpXIgPZGlG4/edit?usp=sharing}{\color{blue!70}{V2]}}
\end{itemize}}

\cventry{}{- ML from a CV and NLP perspective}{at Qube Cinema Technologies - Offsite 2016 \href{https://github.com/tpsatish95/talks/blob/master/ML\%20from\%20a\%20CV\%20and\%20NLP\%20perspective.pdf}{\color{blue!70}{[slide deck]}}}{}{}{}

\cventry{}{- Python Hands-on}{Two-day workshop, at ACM Student Chapter, SSN CE \href{https://github.com/tpsatish95/Python-Workshop}{\color{blue!70}{[link]}}}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Open Source Contributions}
\cventry{\textbf{Diskoveror}}{Text analytics package}{}{}{}{ 
\begin{itemize}
\item Developed the Topic Modeling and Sentiment Analysis modules in Python. \href{https://github.com/tpsatish95/diskoveror-ml-trainer}{\color{blue!70}{[link]}}
\item Interfaced the Python and existing Java code bases via Facebook's Thrift API. \href{https://github.com/serendio-labs-stage/diskoveror-ta/commits?author=tpsatish95}{\color{blue!70}{[link]}}
\end{itemize}
}
\cventry{\textbf{RealImage}}{Algorithm for territorial restriction of film distribution rights}{Challenge 2016}{}{}{ 
\begin{itemize}
\item Implemented using hash maps, trees, and bit indexes with constant time lookup. \href{https://github.com/RealImage/challenge2016/pull/6}{\color{blue!70}{[link]}}
\end{itemize}
}
\cventry{\textbf{Keras}}{Deep Learning library for Python}{}{}{}{ 
\begin{itemize}
\item Implemented random shear data augmentation technique as a part of the CNN's training pipeline. \href{https://github.com/keras-team/keras/pull/1566}{\color{blue!70}{[link]}}
\end{itemize}
}
\cventry{\textbf{Gensim}}{Topic modeling library for Python}{}{}{}{ 
\begin{itemize}
\item Ported the phrase vector representation technique of word2vec word vectors, from C to Python. \href{https://github.com/RaRe-Technologies/gensim/pull/395}{\color{blue!70}{[link]}}
\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\cvitem{Languages}{Python, Java, C, C++, VB.Net, R}
\cvitem{Libraries}{\textsc{Caffe, TensorFlow, Keras, OpenCV}, Scikit-Learn, NLTK}
\cvitem{Others}{Linux, Android SDK, Git, \LaTeX, Docker, Adobe Photoshop}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership and Professional Affiliations}

\cventry{2018 - Present}{Course Assistant}{Object-Oriented Software Engineering (EN601.421/621 )}{JHU}{}{}

\cventry{2014 - 2016}{Association for Computing Machinery (ACM)}{Student Chapter}{SSN CE}{}{
\begin{itemize}
\item Roles: \textbf{Chairman} (2015 to 2016), \textbf{Treasurer and Tech Lead} (2014 to 2015)
\end{itemize}}

\cventry{2014 - 2015}{Google Student Club (GSC)}{Tech Lead}{SSN CE}{}{}

\cventry{2015 - 2016}{Placement Cell}{Student Placement Coordinator, Computer Science Department}{SSN CE}{}{}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Standardized Tests}
% \cvitem{\textbf{GRE}}{Score: \textbf{324} / 340
% \newline
% - \textbf{Quantitative:} 169/170, \textbf{Verbal:} 155/170.}
% \
% \cvitem{\textbf{TOEFL}}{Score: \textbf{116} / 120
% \newline
% - \textbf{Reading:} 29/30, \textbf{Listening:} 30/30, \textbf{Speaking:} 28/30, \textbf{Writing:} 29/30.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\centering
\cvitem{}{
\centering
\begin{tabularx}{450pt}{@{\extracolsep{\fill}}>{\centering\arraybackslash}c c c} 
Deep Learning & Probabilistic Models of the Visual Cortex & Neuro Data Design\\
Prof. Gregory Hager & Prof. Alan L. Yuille  & Prof. Joshua Vogelstein \\
EN.601.682 & AS.050.675 & EN.580.697
\end{tabularx}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage


\end{document}